%----------------------------------------------------------------------------------------
% 
% LaTeX CV class: xqcv 
% author: Xian Qiu
% version: beta 0
%
% Note: 1. do not use \subsubsection.
%       2. itemized lists should not be more than two levels
%       3. publications must be compiled by biber.
%
% any problem? do not ask me. 
%
%----------------------------------------------------------------------------------------


\documentclass[showupdate]{xqcv}
% two options: <print> -- header is not filled 
%              <showupdate> -- update date is shown in the header


%----------------------------------------------------------------------------------------
% bibliography classifications
%----------------------------------------------------------------------------------------


% Specify the bibliography file to include publications
\bibliography{bibliography.bib} 
\addtocategory{papers}{tomov2016distinct, wang2016detecting, Nalbantoglu201442, Isci15032014, Dogan2014genome}
% \addtocategory{proceedings}{KEQI11a, KEQI11b,KEQI13a}
% \addtocategory{workingpapers}{KEQI13b}
\addtocategory{chapters}{Dogan2014objective}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
% header
%----------------------------------------------------------------------------------------


\name{Haluk}{Dogan} % first name and last name
% \currentposition{PhD at University of Nebraska-Lincoln} % current job title/field
% contact info
\address{1432 B St Apt 2\\
         Lincoln, Nebraska 68502, USA
       }
\phonenumber{(402) 419-8475} % phone number
\email{hlk.dogan@gmail.com}  % email address
% \homepage{http://goo.gl/hO4HF} % homepage
\headerboxheight{6cm} % this defines the height of shading


\maketitle

\section{Research Interests}
Machine learning, graphical models, graph algorithms, functional programming.

%----------------------------------------------------------------------------------------
% education
%----------------------------------------------------------------------------------------
\section{Education}
\begin{entrylist}
  \entry
  {2013 -}
  {\textbf{Doctor of Philosophy}}
  {University of Nebraska-Lincoln, USA}
  {
    \textit{Department of Electrical and Computer Engineering}
  }
  \entry
  {2011 - 2013}
  {\textbf{Master of Science}}
  {Bogazici University, Istanbul - Turkey}
  {
   \textit{Department of Computer Engineering} \\
   \textit{\footnotesize{Thesis: Discovering Gene Interaction Atlas Using External Biological Knowledge}}
   }
   \entry
   {2008 - 2009}
   {\textbf{Exchange Student}}
   {Aarhus University, Denmark}
   {
    \textit{Department of Computer Science}
   }
  \entry
  {2006 - 2010}
  {\textbf{Bachelor of Science}}
  {Istanbul Bilgi University - Turkey}
  {\textit{Department of Computer Science}}
\end{entrylist}

\section{Employment History}
\begin{entrylist}
  \hentry
  {Aug 2013 -}
  {\textbf{University Of Nebraska-Lincoln, Lincoln, NE}}
  {\textit{Graduate Research Assistant, Department of Electrical and Computer Engineering}}
  {}

  \hentry
  {Nov 2010 - Jun 2013}
  {\textbf{Istanbul Bilgi University, Istanbul, Turkey}}
  {\textit{Teaching and Research Assistant, Department of Genetics and Bioengineering Engineering}}
  {
    \begin{itemize}
      \item \textbf{BIOE 341}, Bioinformatics; Led weekly lab, and office hours, grading (quizzes, homework assignments, projects, midterms), and proctored exams.
      \item \textbf{CMPE 100}, Introduction to Computing; Led weekly lab, and office hours, grading (quizzes, homework assignments, projects), and proctored exams.
      \item \textbf{ENGR 230}, Probability and Random Processes; Led weekly lab, and office hours, grading (quizzes, homework assignments, projects, midterms), and proctored exams.
      \item Built an interactive ICGEB 2012 Workshop website using Django Web Framework.
    \end{itemize}
  }

  \hentry
  {Mar 2010 - Jun 2010}
  {\textbf{i2i Systems, Istanbul, Turkey}}
  {Java Developer}
  {My responsibilities included importing large dataset into Oracle database after post stage of data preprocessing. The facilitating technologies were Java, Spring Framework, and JExcel.}

  \hentry
  {Aug 2009 - Mar 2010}
  {\textbf{GNA, Istanbul, Turkey}}
  {Business Intelligence Consultant}
  {
    \begin{itemize}
      \item Design, develop, and support Pentaho Reports applications used by business users at a large company setting.
      \item Design, develop, and support creation of tables, stored procedures, functions, views, triggers, and all relevant database objects using Oracle database.
    \end{itemize}
  }
  
  \hentry
  {Mar 2008 - June 2008}
  {\textbf{Aradiom, Istanbul, Turkey}}
  {Java Developer}
  {
    Designed and implemented back-end RegEx editor using JSF framework. My responsibilities were focused on parsing various statements into RegEx expressions.
  }

\end{entrylist}

% \subsection{Certificates}

% \begin{entrylist}
%   \entry
%   {2010-2013}
%   {LNMB diploma}
%   {Utrecht University, The Netherlands}
%   {LNMB: Dutch Network on the Mathematics of Operations Research}
%   \entry
%   {2008}
%   {International Engish language test, grade 7 (over 10)}
%   {IELTS}
%   {}
% \end{entrylist}

% \section{Awards} 
 
% \begin{entrylist}
%   \entry
%   {2008-2012}
%   {National scholarship, \officialeuro 1200/month}
%   {China Scholarship Council}
%   {}
%   \entry
%   {2008-2010}
%   {UT scholarship, \officialeuro 10,000/year}
%   {University of Twente}
%   {}
%   \entry
%   {2004-2006}
%   {NPU scholarship, first grade, RMB 1,000/year}
%   {Northwestern Polytechnical University}
%   {}
%   \entry
%   {2006}
%   {First prize of the ``math modeling'' competition}
%   {Northwestern Polytechnical University}
%   {}
%   \entry
%   {2004}
%   {AMECO scholarship, RMB 1,000}
%   {Northwestern Polytechnical University}
%   {10 out of 3000 students}
% \end{entrylist}

\section{Project Summary}
\begin{itemize}
  \item \footnotesize{Implemented and designed I/O-efficient merge-sort algorithm.}
  \item \footnotesize{Implemented and designed I/O-efficient heap and heap sort algorithm.}
  \item \footnotesize{Implemented offline and online versions of minimum spanning tree problem using sparsification technique.}
  \item \footnotesize{Implemented and designed McCreight's suffix tree construction algorithm.}
  \item \footnotesize{Implemented and designed Stoye-Gusfield algorithm for finding all occurrences of tandem repeats.}
  \item \footnotesize{Designed a distributed application that sends SMS messages by connecting to SMSC via SMPP by using Apache Thrift RPC Framework.}
  \item \footnotesize{Implemented and designed J48 decision tree.}
  \item \footnotesize{Implemented and designed Huffman Coding and Arithmetic Coding algorithms.}
  \item \footnotesize{Implemented and designed Multi-Layer Perceptron Neural Network for classification.}
  \item \footnotesize{Implemented and designed N\"{a}ive Bayes algorithm for classification.}
  \item \footnotesize{Implemented and designed Non-parametric Bayesian Method for clustering.}
\end{itemize}

\section{Skills Summary}
\begin{entrylist}
  \lentry{Programming Languages}{Java, Python, Scala, R, Scheme, C, Haskell, SQL} \\                       
  \lentry{Script Languages}{Bash Script, \LaTeX$\backslash$Tikz, Markdown}  
  \lentry{Database Systems}{Oracle, PostgreSQL, MySQL}
  \lentry{Web Development}{Django Web Framework, Vaadin RIA Web Framework, Spring MVC}
  \lentry{Database Technologies}{Hibernate ORM, SQLAlchemy}
  \lentry{Scientific Programming}{Numpy, Scipy, Scikit-Learn, Matplotlib, Seaborn, Smile, aGrUM, Tetrad}  
  \lentry{Development Technologies}{PyCharm, IntelliJ IDEA, DataGrip, Eclipse, Sublime Text Editor, Atom, Aqua Studio, Weka, RStudio, Matlab}
  \lentry{Build Tools}{Maven, Sbt, Gradle, SCons, CMake}
  \lentry{Version Control System}{Git, SVN, Mercurial}
  \lentry{Operating Systems}{Linux, Mac OS X, Windows}
  \lentry{Foreign Language Skills}{Turkish \rtext{Native}\\
                     English \rtext{Advanced}\\
                     Danish/German \rtext{Beginner}}
\end{entrylist}

\newpage
\section{Publications}
\printbib{papers}
\printbib{chapters}

\section{References}
\textit{References available upon request.}
\end{document}